---
title: "Assignment 6: Relational data plus revisiting data wrangling and visualization"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##**Instructions: Please read through this before you begin**


* This assignment is due by **10pm on Monday 11/02/20.**

* Please **reproduce this markdown template.** Pay attention to all the formating in this file, including bullet points, bolded characters, inserted code chunks, headings, text colors, blank lines, and etc.

* For exercise 1 use the apppropriate `join` function to join some relational datasets, and use the resulting datasets to answer some questions.

* Have all your code embedded within the R markdown file, and show both of your **code** and **plots** in the knitted markdown file.

* Use R Markdown functionalities to **hide messages and warnings when needed.** (Suggesstion: messages and warnings can often be informative and important, so please examine them carefully and only turn them off when you finish the exercise).

* Please name your R markdown file `assignment_6.Rmd` and the knitted markdown `assignment_6.md.` Please upload both files using your personal GitHub repository for this class. 

* First, load all the required packages with the following code. Install them if they are not installed yet.


```{r}

library(tidyverse)
library(knitr)

```


## **Exercise 1: Join functions**

**Acknowledgments:** The datasets and some of the questions for this exercise has been borrowed (with permission) from lain Carmichael's course STOR 290: Introduction to Data Science.

**Read in some relational datasets from GitHub**

```{r}

## for 4.1
toy1 <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/toy_one.csv')
toy2 <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/toy_two.csv')

## for 4.2
play1 <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/play_one.csv')
play2 <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/play_two.csv')

## for 4.3
banking_account_types <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/banking_account_types.csv')
banking_transactions <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/banking_transactions.csv')

## for 4.4
crime_arrests <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/crime_arrests.csv')
crime_wealth <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/crime_wealth.csv')

## for 4.5
titanic_outcomes <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/titanic_outcomes.csv')
titanic_person_features <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/titanic_person_features.csv')


```




**1.1 Join the `toy` datasets. Only keep rows that have matches in the other dataset. Show the resulting dataset using `kable()`.**

```{r}
toy3<-toy1 %>% 
  left_join(toy2, c("key" = "label"))%>% 
  kable()


```
















