---
title: "Assignment 6: Relational data plus revisiting data wrangling and visualization"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##**Instructions: Please read through this before you begin**


* This assignment is due by **10pm on Monday 11/02/20.**

* Please **reproduce this markdown template.** Pay attention to all the formating in this file, including bullet points, bolded characters, inserted code chunks, headings, text colors, blank lines, and etc.

* For exercise 1 use the apppropriate `join` function to join some relational datasets, and use the resulting datasets to answer some questions.

* Have all your code embedded within the R markdown file, and show both of your **code** and **plots** in the knitted markdown file.

* Use R Markdown functionalities to **hide messages and warnings when needed.** (Suggesstion: messages and warnings can often be informative and important, so please examine them carefully and only turn them off when you finish the exercise).

* Please name your R markdown file `assignment_6.Rmd` and the knitted markdown `assignment_6.md.` Please upload both files using your personal GitHub repository for this class. 

* First, load all the required packages with the following code. Install them if they are not installed yet.


```{r}

library(tidyverse)
library(knitr)

```


## **Exercise 1: Join functions**

**Acknowledgments:** The datasets and some of the questions for this exercise has been borrowed (with permission) from lain Carmichael's course STOR 290: Introduction to Data Science.

**Read in some relational datasets from GitHub**

```{r}

## for 4.1
toy1 <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/toy_one.csv')
toy2 <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/toy_two.csv')

## for 4.2
play1 <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/play_one.csv')
play2 <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/play_two.csv')

## for 4.3
banking_account_types <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/banking_account_types.csv')
banking_transactions <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/banking_transactions.csv')

## for 4.4
crime_arrests <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/crime_arrests.csv')
crime_wealth <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/crime_wealth.csv')

## for 4.5
titanic_outcomes <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/titanic_outcomes.csv')
titanic_person_features <- read_csv('https://raw.githubusercontent.com/idc9/stor390/master/data/joins/titanic_person_features.csv')


```




**1.1 Join the `toy` datasets. Only keep rows that have matches in the other dataset. Show the resulting dataset using `kable()`.**

```{r}
toy1 %>% 
  left_join(toy2, c("key" = "label")) %>% 
  na.omit() %>% 
  kable()


```


**1.2. Join the `play` datasets by `key` and `label`. Keep all rows from both datasets. Show the resulting dataset using `kable()`.


```{r}
play1 %>% 
  left_join(play2, by = c("key","label")) %>% 
kable()
```


**1.3. Plot the distribution of total transaction amount per account ID grouped by different account types with a boxplot shown below, using the `banking` datasets.**


```{r,message= F}

banking_account_types %>% 
  left_join(banking_transactions, c("account_id" = "id")) %>% 
  group_by(account_type, account_id) %>% 
  summarise(total_transaction_ammount = sum(transaction_amount)) %>% 
  ggplot(mapping = aes(x = account_type, y = total_transaction_ammount)) +
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(height = 0)
  
```


**1.4 Which state is in the `crime_wealth`dataset but not the `crime_arrests` dataset? Use a join function to answer this question**

District of Columbia is in crime_wealth dataset but not in crime_arrests data set.


```{r}

crime_wealth %>% 
  anti_join(crime_arrests, by = "State") %>% 
  kable()

```


**1.5 OPTIONAL:****Plot the number of passenger who did and did not survive, grouped by their classes, using`titanic` data sets**


```{r}

titanic_person_features2 <- titanic_person_features %>% 
  select(PID, PClass) 
#View(titanic_person_features2)

titanic_person_features2 %>% 
  left_join(titanic_outcomes, by = "PID") %>% 
  group_by(PClass) %>% 
  ggplot(mapping = aes(x = PClass, fill = Survived)) +
  geom_bar() 

```



##**Excercise 2: Fuel Efficeincy of Car Models**

This exercise uses the `mtcars` dataset. It was extracted from the 1974 Motor Trend US 
magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

```{r}
kable(head(mtcars))
```


**Reproduce the following plot, which shows the miles per gallon (mpg) of car models on the x axis (see hints below). Different models are ordered on the y axis according to their `mpg` and their names are shown next to the data points. Also, the size of each data point maps to its horse power (`hp`), and the color maps to number of cylinders (`cyl`). 


```{r}

mtcars1<-rownames_to_column(mtcars) 
mtcars2<-mtcars1 %>% 
  mutate(mpg_order = row_number(mtcars1$mpg)) %>% 
  select(rowname,mpg, mpg_order, cyl, hp) 
  kable(head(mtcars2))


```



**Hint1: Start by transforming the data frame into the following format.**

* Convert rownames to a column. (`rownames_to_column() might be helpful)
* create a new varible which shows the order of car models based on their mpg. (`row_number()`) might be helpful).

the first few rows of this new data frame might look like the following.




**Hint2: When making the plot, pay attention to the following elements of the plot that need to be specified.**

* Horizontal adjustment of the text labels ("hjust" option in `geom_text()`)

* The range of the x-axis (`xlim()`)

* x-axis label and legend titles (`labs()`)

* The removal of the y-axis (`theme()`)











